The Sub-Millimetre User Reduction Facility: an iterative map-maker for SCUBA-2

### 2010-11-24 smurf_paper.tex
add flowchart to describe iterative map-maker

% common acronyms etc.
\newcommand{\snr}{SNR}
\newcommand{\scuba}{SCUBA-2}

@@

\begin{itemize}
\item minimize excess whitespace around the figure to optimize usage of space
\item ensure a decent line thickness
\item use a Times font for labels with a thickness that resembles the
  text in the body. The font size should be the same as the main body
  text or larger
\item avoid using colour unless it is necessary for emphasis
\end{itemize}

@@

\begin{figure}
\centering
\includegraphics[width=0.99\linewidth]{bolos_point_mix.pdf}
\caption{A comparison between single bolometer time series in each
  band (top two plots), with the mixing chamber temperature and
  azimuth/elevation pointing offsets. There is a strong correlation
  between the bolometers and the roughly $\sim$30\,s oscillation in
  the fridge, but not with the telescope motion. Also note that the
  total power in this primary signal is similar at both 450 and
  850\,\micron, pointing to an internal rather than an external
  source.}
\label{fig:bolos_mix}
\end{figure}

@@

>>>>

% common acronyms etc.
\newcommand{\snr}{SNR}
\newcommand{\scuba}{SCUBA-2}
\newcommand{\rms}{RMS}

@@

\begin{itemize}
\item minimize excess whitespace around the figure to optimize usage of space
\item ensure a decent line thickness
\item use a Times font for labels with a thickness that resembles the
  text in the body. The font size should be similar to the main body
  text or larger
\item avoid using colour unless it is necessary for emphasis
\end{itemize}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{bolos_point_mix.pdf}
\caption{A comparison between single bolometer time series in each
  band (top two plots), with the mixing chamber temperature and
  azimuth/elevation pointing offsets. There is a strong correlation
  between the bolometers and the roughly $\sim$25\,s oscillation in
  the fridge, but not with the telescope motion. Also note that the
  total power in this primary signal is similar at both 450 and
  850\,\micron, pointing to an internal rather than an external
  source.}
\label{fig:bolos_mix}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\linewidth]{dimm.pdf}
\caption{Typical map-making algorithm. Raw data (stored in multiple
  files) are read and concatenated into continuous time series. A
  pre-processing stage repairs DC steps, applies a flatfield
  correction, identifies and removes the noisiest bolometers, and
  flags large spikes. The iterative portion then begins: estimating
  and removing the common-mode signal; applying the extinction
  correction; high-pass filtering to remove residual independent
  low-frequency noise; estimating the map by re-gridding the data; and
  finally measuring the noise in the residual time series. If the
  \rms\ has converged, the final map is written to disk. Otherwise any
  multiplicative factors that may have been applied to the data are
  inverted (e.g., extinction correction and relative gains measured
  during the common-mode calculation), and each additive component is
  added back into the time series and re-estimated in turn.}
\label{fig:dimm}
\end{figure}
